\chapter{Topic overviews}
\setheader{{\it CHAPTER \thechapter}}{}{}{}{}{{\it CHAPTER \thechapter}}%
\setfooter{\thepage}{}{}{}{}{\thepage}

The following sections describe particular topics.

\section{OGL overview}\label{ogloverview}

\helpref{wxShapeCanvas}{wxshapecanvas}, derived from {\bf wxCanvas}, is the drawing area
for a number of \helpref{wxShape}{wxshape} instances. Everything drawn on a
wxShapeCanvas is derived from wxShape, which provides virtual
member functions for redrawing, creating and destroying
resize/selection `handles', movement and erasing behaviour, mouse
click behaviour, calculating the bounding box of the shape, linking
nodes with arcs, and so on.

The way a client application copes with `damage' to the canvas is to
erase (white out) anything should no longer be displayed, redraw the shape,
and then redraw everything on the canvas to repair any damage. If quick edit
mode is on for the canvas, the complete should be omitted by OGL and the
application.

Selection handles (called control points in the code) are implemented as
wxRectangleShapes.

Events are passed to shapes by the canvas in a high-level form, for example {\bf OnLeftClick},
{\bf OnBeginDragLeft}, {\bf OnDragLeft}, {\bf OnEndDragLeft}. The canvas decides
what is a click and what is a drag, whether it is on a shape or the canvas itself,
and (by interrogating the shape) which attachment point the click is associated with.

In order to provide event-handling flexibility, each shapes has an `event handler' associated with it,
which by default is the shape itself (all shapes derive from wxShapeEvtHandler).
An application can modify the event-handling behaviour simply by plugging a new
event handler into the shape. This can avoid the need for multiple inheritance when
new properties and behaviour are required for a number of different shape classes: instead
of overriding each class, one new event handler class can be defined and used for all
existing shape classes.

A range of shapes have been predefined in the library, including rectangles, ellipses,
polygons. A client application can derive from these shapes and/or derive entirely
new shapes from wxShape.

Instances of a class called \helpref{wxDiagram}{wxdiagram} organise collections of
shapes, providing default file input and output behaviour.


\section{wxDividedShape overview}\label{dividedshapeoverview}

Classes: \helpref{wxDividedShape}{wxdividedshape}

A wxDividedShape is a rectangle with a number of vertical divisions. Each
division may have its text formatted with independent characteristics, and
the size of each division relative to the whole image may be specified.

Once a wxDividedShape has been created, the user may move the divisions with the
mouse. By pressing Ctrl while right-clicking, the region attributes can be edited.

Here are examples of creating wxDividedShape objects:

{\small
\begin{verbatim}
  /*
   * Divided rectangle with 3 regions
   *
   */

  wxDividedShape *dividedRect = new wxDividedShape(50, 60);

  wxShapeRegion *region = new wxShapeRegion;
  region->SetProportions(0.0, 0.25);
  dividedRect->AddRegion(region);

  region = new wxShapeRegion;
  region->SetProportions(0.0, 0.5);
  dividedRect->AddRegion(region);

  region = new wxShapeRegion;
  region->SetProportions(0.0, 0.25);
  dividedRect->AddRegion(region);
  
  dividedRect->SetSize(50, 60); // Allow it to calculate region sizes
  dividedRect->SetPen(wxBLACK_PEN);
  dividedRect->SetBrush(wxWHITE_BRUSH);
  dividedRect->Show(TRUE);
  dividedRect->NameRegions();

  /*
   * Divided rectangle with 3 regions, rounded
   *
   */

  wxDividedShape *dividedRect3 = new wxDividedShape(50, 60);
  dividedRect3->SetCornerRadius(-0.4);

  region = new wxShapeRegion;
  region->SetProportions(0.0, 0.25);
  dividedRect3->AddRegion(region);

  region = new wxShapeRegion;
  region->SetProportions(0.0, 0.5);
  dividedRect3->AddRegion(region);

  region = new wxShapeRegion;
  region->SetProportions(0.0, 0.25);
  dividedRect3->AddRegion(region);
  
  dividedRect3->SetSize(50, 60); // Allow it to calculate region sizes
  dividedRect3->SetPen(wxBLACK_PEN);
  dividedRect3->SetBrush(wxWHITE_BRUSH);
  dividedRect3->Show(TRUE);
  dividedRect3->NameRegions();
\end{verbatim}
}


\section{wxCompositeShape overview}\label{compositeshapeoverview}

Classes: \helpref{wxCompositeShape}{wxcompositeshape}, \helpref{OGLConstraint}{oglconstraint}

The wxCompositeShape allows fairly complex shapes to be created, and maintains
a set of constraints which specify the layout and proportions of child shapes.

Add child shapes to a wxCompositeShape using \helpref{AddChild}{wxcompositeshapeaddchild}, and
add constraints using \helpref{AddConstraint}{wxcompositeshapeaddconstraint}.

After children and shapes have been added, call \helpref{Recompute}{wxcompositeshaperecompute} which
will return TRUE is the constraints could be satisfied, FALSE otherwise. If
constraints have been correctly and consistently specified, this call will succeed.

If there is more than one child, constraints must be specified: OGL cannot calculate
the size and position of children otherwise. Don't assume that children will simply
move relative to the parent without the use of constraints.

To specify a constraint, you need three things:

\begin{enumerate}\itemsep=0pt
\item a constraint type, such as gyCONSTRAINT\_CENTRED\_VERTICALLY;
\item a reference shape, with respect to which other shapes are going to be positioned - the\rtfsp
{\it constraining} shape;
\item a list of one or more shapes to be constrained: the {\it constrained} shapes.
\end{enumerate}

The constraining shape can be either the parent of the constrained shapes, or a sibling. The
constrained shapes must all be siblings of each other.

For an exhaustive list and description of the available constraint types, see the \helpref{OGLConstraint constructor}{oglconstraintconstr}.
Note that most constraints operate in one dimension only (vertically or horizontally), so you will
usually need to specify constraints in pairs.

You can set the spacing between constraining and constrained shapes by
calling \helpref{OGLConstraint::SetSpacing}{oglconstraintsetspacing}.

Finally, a wxCompositeShape can have {\it divisions}, which are special child shapes of class
wxDivisionShape (not to be confused with wxDividedShape). The purpose of this is to allow
the composite to be divided into user-adjustable regions (divisions) into which other shapes
can be dropped dynamically, given suitable application code. Divisons allow the child
shapes to have an identity of their own - they can be manipulated independently of their container -
but to behave as if they are contained with the division, moving with the parent shape.
Divisions boundaries can themselves be moved using the mouse.

To create an initial division, call \helpref{wxCompositeShape::MakeContainer}{wxcompositeshapemakecontainer}.
Make further divisions by calling \helpref{wxDivisionShape::Divide}{wxdivisionshapedivide}.

