\chapter{Introduction}
\pagenumbering{arabic}%
\setheader{{\it CHAPTER \thechapter}}{}{}{}{}{{\it CHAPTER \thechapter}}%
\setfooter{\thepage}{}{}{}{}{\thepage}

Object Graphics Library (\ogl) is a C++ library supporting the creation and
manipulation of simple and complex graphic images on a canvas.

It can be found in the directory {\tt utils/ogl/src} in the
wxWindows distribution. The file {\tt ogl.h} must be included to make use
of the library.

Please see \helpref{OGL overview}{ogloverview} for a general description how the object library works. For details,
please see the \helpref{class reference}{classref}.

\section{File structure}

These are the files that comprise the \ogl\ library.

\begin{description}\itemsep=0pt
\item[basic.h] Header for basic objects such as wxShape and wxRectangleShape.
\item[basic.cpp] Basic objects implementation (1).
\item[basic2.cpp] Basic objects implementation (2).
\item[bmpshape.h] wxBitmapShape class header.
\item[bmpshape.cpp] wxBitmapShape implementation.
\item[canvas.h] wxShapeCanvas class header.
\item[canvas.cpp] wxShapeCanvas class implementation.
\item[composit.h] Composite object class header.
\item[composit.cpp] Composite object class implementation.
\item[constrnt.h] Constraint classes header.
\item[constrnt.cpp] Constraint classes implementation.
\item[divided.h] Divided object class header.
\item[divided.cpp] Divided object class implementation.
\item[drawn.h] Drawn (metafile) object class header.
\item[drawn.cpp] Drawn (metafile) object class implementation.
\item[graphics.h] Main include file.
\item[lines.h] wxLineShape class header.
\item[lines.cpp] wxLineShape class implementation.
\item[misc.h] Miscellaneous graphics functions header.
\item[misc.cpp] Miscellaneous graphics functions implementation.
\item[ogldiag.h] wxDiagram class header.
\item[ogldiag.cpp] wxDiagram implementation.
\item[mfutils.h] Metafile utilities header.
\item[mfutils.cpp] Metafile utilities implementation.
\end{description}


