\section{Event macros and identifiers}\label{events}

These are the event macros and event identifiers defined by FL.

\twocolwidtha{7cm}
\begin{twocollist}\itemsep=0pt
\twocolitemruled{{\bf Event macro}}{{\bf Event identifier}}
\twocolitem{EVT\_PL\_LEFT\_DOWN(func)}{cbEVT\_PL\_LEFT\_DOWN}
\twocolitem{EVT\_PL\_LEFT\_UP(func)}{cbEVT\_PL\_LEFT\_UP}
\twocolitem{EVT\_PL\_RIGHT\_DOWN(func)}{cbEVT\_PL\_RIGHT\_DOWN}
\twocolitem{EVT\_PL\_RIGHT\_UP(func)}{cbEVT\_PL\_RIGHT\_UP}
\twocolitem{EVT\_PL\_MOTION(func)}{cbEVT\_PL\_MOTION}
\twocolitem{EVT\_PL\_LEFT\_DCLICK(func)}{cbEVT\_PL\_LEFT\_DCLICK}

\twocolitem{EVT\_PL\_LAYOUT\_ROW(func)}{cbEVT\_PL\_LAYOUT\_ROW}
\twocolitem{EVT\_PL\_RESIZE\_ROW(func)}{cbEVT\_PL\_RESIZE\_ROW}
\twocolitem{EVT\_PL\_LAYOUT\_ROWS(func)}{cbEVT\_PL\_LAYOUT\_ROWS}
\twocolitem{EVT\_PL\_INSERT\_BAR(func)}{cbEVT\_PL\_INSERT\_BAR}
\twocolitem{EVT\_PL\_RESIZE\_BAR(func)}{cbEVT\_PL\_RESIZE\_BAR}
\twocolitem{EVT\_PL\_REMOVE\_BAR(func)}{cbEVT\_PL\_REMOVE\_BAR}
\twocolitem{EVT\_PL\_SIZE\_BAR\_WND(func)}{cbEVT\_PL\_SIZE\_BAR\_WND}

\twocolitem{EVT\_PL\_DRAW\_BAR\_DECOR(func)}{cbEVT\_PL\_DRAW\_BAR\_DECOR}
\twocolitem{EVT\_PL\_DRAW\_ROW\_DECOR(func)}{cbEVT\_PL\_DRAW\_ROW\_DECOR}
\twocolitem{EVT\_PL\_DRAW\_PANE\_DECOR(func)}{cbEVT\_PL\_DRAW\_PANE\_DECOR}
\twocolitem{EVT\_PL\_DRAW\_BAR\_HANDLES(func)}{cbEVT\_PL\_DRAW\_BAR\_HANDLES}
\twocolitem{EVT\_PL\_DRAW\_ROW\_HANDLES(func)}{cbEVT\_PL\_DRAW\_ROW\_HANDLES}
\twocolitem{EVT\_PL\_DRAW\_ROW\_BKGROUND(func)}{cbEVT\_PL\_DRAW\_ROW\_BKGROUND}
\twocolitem{EVT\_PL\_DRAW\_PANE\_BKGROUND(func)}{cbEVT\_PL\_DRAW\_PANE\_BKGROUND}

\twocolitem{EVT\_PL\_START\_BAR\_DRAGGING(func)}{cbEVT\_PL\_START\_BAR\_DRAGGING}
\twocolitem{EVT\_PL\_DRAW\_HINT\_RECT(func)}{cbEVT\_PL\_DRAW\_HINT\_RECT}

\twocolitem{EVT\_PL\_START\_DRAW\_IN\_AREA(func)}{cbEVT\_PL\_START\_DRAW\_IN\_AREA}
\twocolitem{EVT\_PL\_FINISH\_DRAW\_IN\_AREA(func)}{cbEVT\_PL\_FINISH\_DRAW\_IN\_AREA}

\twocolitem{EVT\_PL\_CUSTOMIZE\_BAR(func)}{cbEVT\_PL\_CUSTOMIZE\_BAR}
\twocolitem{EVT\_PL\_CUSTOMIZE\_LAYOUT(func)}{cbEVT\_PL\_CUSTOMIZE\_LAYOUT}
\end{twocollist}

See also the classes:

\twocolwidtha{7cm}
\begin{twocollist}\itemsep=0pt
\twocolitem{\helpref{cbCustomizeBarEvent}{cbcustomizebarevent}}{Class for bar customization events.}
\twocolitem{\helpref{cbCustomizeLayoutEvent}{cbcustomizelayoutevent}}{Class for layout customization events.}
\twocolitem{\helpref{cbDrawBarDecorEvent}{cbdrawbardecorevent}}{Class for bar decoration drawing events.}
\twocolitem{\helpref{cbDrawBarHandlesEvent}{cbdrawbarhandlesevent}}{Class for bar handles drawing events.}
\twocolitem{\helpref{cbDrawHintRectEvent}{cbdrawhintrectevent}}{Class for hint-rectangle drawing events.}
\twocolitem{\helpref{cbDrawPaneBkGroundEvent}{cbdrawpanebkgroundevent}}{Class for pane background drawing events.}
\twocolitem{\helpref{cbDrawPaneDecorEvent}{cbdrawpanedecorevent}}{Class for pane decoration drawing events.}
\twocolitem{\helpref{cbDrawRowBkGroundEvent}{cbdrawrowbkgroundevent}}{Class for row background drawing events.}
\twocolitem{\helpref{cbDrawRowDecorEvent}{cbdrawrowdecorevent}}{Class for row decoration drawing events.}
\twocolitem{\helpref{cbDrawRowHandlesEvent}{cbdrawrowhandlesevent}}{Class for row handles drawing events.}
\twocolitem{\helpref{cbFinishDrawInAreaEvent}{cbfinishdrawinareaevent}}{Class for finish drawing in area events.}
\twocolitem{\helpref{cbInsertBarEvent}{cbinsertbarevent}}{Class for bar insertion events.}
\twocolitem{\helpref{cbLayoutRowEvent}{cblayoutrowevent}}{Class for single row layout events.}
\twocolitem{\helpref{cbLayoutRowsEvent}{cblayoutrowsevent}}{Class for multiple rows layout events.}
\twocolitem{\helpref{cbLeftDClickEvent}{cbleftdclickevent}}{Class for mouse left double click events.}
\twocolitem{\helpref{cbLeftDownEvent}{cbleftdownevent}}{Class for mouse left down events.}
\twocolitem{\helpref{cbLeftUpEvent}{cbleftupevent}}{Class for mouse left up events.}
\twocolitem{\helpref{cbMotionEvent}{cbmotionevent}}{Class for mouse motion events.}
\twocolitem{\helpref{cbPluginEvent}{cbpluginevent}}{Base class for all control-bar plugin events.}
\twocolitem{\helpref{cbRemoveBarEvent}{cbremovebarevent}}{Class for bar removal events.}
\twocolitem{\helpref{cbResizeBarEvent}{cbresizebarevent}}{Class for bar resize events.}
\twocolitem{\helpref{cbResizeRowEvent}{cbresizerowevent}}{Class for row resize events.}
\twocolitem{\helpref{cbRightDownEvent}{cbrightdownevent}}{Class for mouse right down events.}
\twocolitem{\helpref{cbRightUpEvent}{cbrightupevent}}{Class for mouse right up events.}
\twocolitem{\helpref{cbSizeBarWndEvent}{cbsizebarwndevent}}{Class for bar window resize events.}
\twocolitem{\helpref{cbStartBarDraggingEvent}{cbstartbardraggingevent}}{Class for start-bar-dragging events.}
\twocolitem{\helpref{cbStartDrawInAreaEvent}{cbstartdrawinareaevent}}{Class for start drawing in area events.}
\end{twocollist}

