\chapter{Change log}\label{changes}
\setheader{{\it CHAPTER \thechapter}}{}{}{}{}{{\it CHAPTER \thechapter}}%
\setfooter{\thepage}{}{}{}{}{\thepage}%

April 22nd, 2000 Version 2.1

\begin{itemize}\itemsep=0pt
\item Various bug fixes.
\item Added buttons for distributing space horizontally and vertically, and
for copying width and height independently.
\item Added 'Convert old resources' facility.
\end{itemize}

December 31st 1998, Version 2.0

\begin{itemize}\itemsep=0pt
\item wxWindows 2.0 port.
\item Major user interface changes.
\item Allows identifiers to be edited and reads/writes an id header file.
\end{itemize}

March 15th 1997, Version 1.7

\begin{itemize}\itemsep=0pt
\item Added fix to wx\_rprop.cpp to avoid Fafa bitmap buttons growing every time the
button edited.
\item Added fix to wx\_resed.cpp, case wxID\_EXIT, to clean up properly on exit, avoiding double deletion of wxBitmap.
\end{itemize}

May 6th 1996, Version 1.6

\begin{itemize}\itemsep=0pt
\item Added panel editing in addition to dialog box editing.
\item Cured some bugs with changing window styles such as wxUSER\_COLOURS and label position.
\item Now preserves syntax of bitmap resources in wxr files.
\end{itemize}

March 1996, Version 1.5

\begin{itemize}\itemsep=0pt
\item Changed behaviour of New tool, and changed File menu to include New project and New dialog items.
Behaviour should be more standard now.
\end{itemize}

March 1st 1996, Version 1.4

\begin{itemize}\itemsep=0pt
\item Items (but not dialogs) can now have duplicate names.
\item Can pass a filename to the program from the command line.
\item Cured bizarre error caused by a Windows combobox sending
a fake left-mouse-up error when losing the focus (switching to another
window). This fix will be in wxWindows 1.66.
\item Rewritten code to use only the new type system, and to take account of
of new window style partitioning (flags for different items may have the same value).
Again, wxWindows 1.66 will have the new style values, to make room for more window
styles.
\end{itemize}

January 28th 1996, Version 1.2

\begin{itemize}\itemsep=0pt
\item Now starts off in non-user-colour mode under Windows
\item Dragging item drags other selected items
\item wxMessage saves size correctly, if used in conjunction with wxWin 1.66
\end{itemize}

January 19th 1996, Version 1.1

\begin{itemize}\itemsep=0pt
\item Cured crash bug when quitting dialog window
\item Added Clear menu item
\item Added window type name to property window
\end{itemize}

December 19th 1995, Version 1.0

\begin{itemize}\itemsep=0pt
\item First release.
\end{itemize}

