
\section{\class{wxDataViewListModelNotifier}}\label{wxdataviewlistmodelnotifier}

A wxDataViewListModelNotifier instance is owned by a
\helpref{wxDataViewListModel}{wxdataviewlistmodel}
and mostly mirrors its interface. See the documentation
of that class for further information.

\wxheading{Derived from}

\helpref{wxObject}{wxobject}

\wxheading{Include files}

<wx/dataview.h>


\membersection{wxDataViewListModelNotifier::wxDataViewListModelNotifier}\label{wxdataviewlistmodelnotifierwxdataviewlistmodelnotifier}

\func{}{wxDataViewListModelNotifier}{\void}

Constructor.

\membersection{wxDataViewListModelNotifier::\destruct{wxDataViewListModelNotifier}}\label{wxdataviewlistmodelnotifierdtor}

\func{}{\destruct{wxDataViewListModelNotifier}}{\void}

Destructor.

\membersection{wxDataViewListModelNotifier::Cleared}\label{wxdataviewlistmodelnotifiercleared}

\func{bool}{Cleared}{\void}

Called by owning list model.

\membersection{wxDataViewListModelNotifier::GetOwner}\label{wxdataviewlistmodelnotifiergetowner}

\func{wxDataViewListModel*}{GetOwner}{\void}

Returns the owning \helpref{wxDataViewListModel}{wxdataviewlistmodel}.

\membersection{wxDataViewListModelNotifier::RowAppended}\label{wxdataviewlistmodelnotifierrowappended}

\func{bool}{RowAppended}{\void}

Called by owning list model.

\membersection{wxDataViewListModelNotifier::RowChanged}\label{wxdataviewlistmodelnotifierrowchanged}

\func{bool}{RowChanged}{\param{unsigned int }{row}}

Called by owning list model.

\membersection{wxDataViewListModelNotifier::RowDeleted}\label{wxdataviewlistmodelnotifierrowdeleted}

\func{bool}{RowDeleted}{\param{unsigned int }{row}}

Called by owning list model.

\membersection{wxDataViewListModelNotifier::RowInserted}\label{wxdataviewlistmodelnotifierrowinserted}

\func{bool}{RowInserted}{\param{unsigned int }{before}}

Called by owning list model.

\membersection{wxDataViewListModelNotifier::RowPrepended}\label{wxdataviewlistmodelnotifierrowprepended}

\func{bool}{RowPrepended}{\void}

Called by owning list model.

\membersection{wxDataViewListModelNotifier::RowsReordered}\label{wxdataviewlistmodelnotifierrowsreordered}

\func{bool}{RowsReordered}{\param{unsigned int* }{new\_order}}

Called by owning list model.

\membersection{wxDataViewListModelNotifier::SetOwner}\label{wxdataviewlistmodelnotifiersetowner}

\func{void}{SetOwner}{\param{wxDataViewListModel* }{owner}}

Set the owning \helpref{wxDataViewListModel}{wxdataviewlistmodel}. This
method is called by the \helpref{wxDataViewListModel::AddNotifier}{wxdataviewlistmodeladdnotifier}.

\membersection{wxDataViewListModelNotifier::ValueChanged}\label{wxdataviewlistmodelnotifiervaluechanged}

\func{bool}{ValueChanged}{\param{unsigned int }{col}, \param{unsigned int }{row}}

Called by owning list model.
