
\section{\class{wxDataViewTreeStore}}\label{wxdataviewtreestore}

wxDataViewTreeStore is a specialised \helpref{wxDataViewModel}{wxdataviewmodel}
for displaying simple trees very much like \helpref{wxTreeCtrl}{wxtreectrl}
does and it offers a similar API. This class actually stores the entire
tree (therefore its name) and implements all virtual from the base class
so it can be used directly without having to derive any class from it.
This comes at the price of much reduced flexibility.

\wxheading{Derived from}

\helpref{wxDataViewModel}{wxdataviewmodel}

\wxheading{Include files}

<dataview.h>

\membersection{wxDataViewTreeStore::wxDataViewTreeStore}\label{wxdataviewtreestorewxdataviewtreestore}

\func{}{wxDataViewTreeStore}{\void}

Constructor. Creates the invisible root node internally.

\membersection{wxDataViewTreeStore::\destruct{wxDataViewTreeStore}}\label{wxdataviewtreestoredtor}

\func{}{\destruct{wxDataViewTreeStore}}{\void}

Destructor.

\membersection{wxDataViewTreeStore::AppendContainer}\label{wxdataviewtreestoreappendcontainer}

\func{wxDataViewItem}{AppendContainer}{\param{const wxDataViewItem\& }{parent}, \param{const wxString\& }{text}, \param{const wxIcon\& }{icon = wxNullIcon}, \param{const wxIcon\& }{expanded = wxNullIcon}, \param{wxClientData* }{data = NULL}}

Append a container.

\membersection{wxDataViewTreeStore::AppendItem}\label{wxdataviewtreestoreappenditem}

\func{wxDataViewItem}{AppendItem}{\param{const wxDataViewItem\& }{parent}, \param{const wxString\& }{text}, \param{const wxIcon\& }{icon = wxNullIcon}, \param{wxClientData* }{data = NULL}}

Append an item.

\membersection{wxDataViewTreeStore::DeleteAllItems}\label{wxdataviewtreestoredeleteallitems}

\func{void}{DeleteAllItems}{\void}

Delete all item in the model.

\membersection{wxDataViewTreeStore::DeleteChildren}\label{wxdataviewtreestoredeletechildren}

\func{void}{DeleteChildren}{\param{const wxDataViewItem\& }{item}}

Delete all children of the item, but not the item itself.

\membersection{wxDataViewTreeStore::DeleteItem}\label{wxdataviewtreestoredeleteitem}

\func{void}{DeleteItem}{\param{const wxDataViewItem\& }{item}}

Delete this item.

\membersection{wxDataViewTreeStore::GetChildCount}\label{wxdataviewtreestoregetchildcount}

\constfunc{int}{GetChildCount}{\param{const wxDataViewItem\& }{parent}}

Return the number of children of item.

\membersection{wxDataViewTreeStore::GetItemData}\label{wxdataviewtreestoregetitemdata}

\constfunc{wxClientData*}{GetItemData}{\param{const wxDataViewItem\& }{item}}

Returns the client data asoociated with the item.

\membersection{wxDataViewTreeStore::GetItemExpandedIcon}\label{wxdataviewtreestoregetitemexpandedicon}

\constfunc{const wxIcon\&}{GetItemExpandedIcon}{\param{const wxDataViewItem\& }{item}}

Returns the icon to display in expanded containers.

\membersection{wxDataViewTreeStore::GetItemIcon}\label{wxdataviewtreestoregetitemicon}

\constfunc{const wxIcon\&}{GetItemIcon}{\param{const wxDataViewItem\& }{item}}

Returns the icon of the item.

\membersection{wxDataViewTreeStore::GetItemText}\label{wxdataviewtreestoregetitemtext}

\constfunc{wxString}{GetItemText}{\param{const wxDataViewItem\& }{item}}

Returns the text of the item.

\membersection{wxDataViewTreeStore::GetNthChild}\label{wxdataviewtreestoregetnthchild}

\constfunc{wxDataViewItem}{GetNthChild}{\param{const wxDataViewItem\& }{parent}, \param{unsigned int }{pos}}

Returns the nth child item of item.

\membersection{wxDataViewTreeStore::InsertContainer}\label{wxdataviewtreestoreinsertcontainer}

\func{wxDataViewItem}{InsertContainer}{\param{const wxDataViewItem\& }{parent}, \param{const wxDataViewItem\& }{previous}, \param{const wxString\& }{text}, \param{const wxIcon\& }{icon = wxNullIcon}, \param{const wxIcon\& }{expanded = wxNullIcon}, \param{wxClientData* }{data = NULL}}

Inserts a container after {\it previous}.

\membersection{wxDataViewTreeStore::InsertItem}\label{wxdataviewtreestoreinsertitem}

\func{wxDataViewItem}{InsertItem}{\param{const wxDataViewItem\& }{parent}, \param{const wxDataViewItem\& }{previous}, \param{const wxString\& }{text}, \param{const wxIcon\& }{icon = wxNullIcon}, \param{wxClientData* }{data = NULL}}

Inserts an item after {\it previous}.

\membersection{wxDataViewTreeStore::PrependContainer}\label{wxdataviewtreestoreprependcontainer}

\func{wxDataViewItem}{PrependContainer}{\param{const wxDataViewItem\& }{parent}, \param{const wxString\& }{text}, \param{const wxIcon\& }{icon = wxNullIcon}, \param{const wxIcon\& }{expanded = wxNullIcon}, \param{wxClientData* }{data = NULL}}

Inserts a container before the first child item or {\it parent}.

\membersection{wxDataViewTreeStore::PrependItem}\label{wxdataviewtreestoreprependitem}

\func{wxDataViewItem}{PrependItem}{\param{const wxDataViewItem\& }{parent}, \param{const wxString\& }{text}, \param{const wxIcon\& }{icon = wxNullIcon}, \param{wxClientData* }{data = NULL}}

Inserts an item before the first child item or {\it parent}.

\membersection{wxDataViewTreeStore::SetItemData}\label{wxdataviewtreestoresetitemdata}

\func{void}{SetItemData}{\param{const wxDataViewItem\& }{item}, \param{wxClientData* }{data}}

Sets the client data associated with the item.

\membersection{wxDataViewTreeStore::SetItemExpandedIcon}\label{wxdataviewtreestoresetitemexpandedicon}

\func{void}{SetItemExpandedIcon}{\param{const wxDataViewItem\& }{item}, \param{const wxIcon\& }{icon}}

Sets the expanded icon for the item.

\membersection{wxDataViewTreeStore::SetItemIcon}\label{wxdataviewtreestoresetitemicon}

\func{void}{SetItemIcon}{\param{const wxDataViewItem\& }{item}, \param{const wxIcon\& }{icon}}

Sets the icon for the item.

\membersection{wxDataViewTreeStore::SetItemText}\label{wxdataviewtreestoresetitemtext}

\func{void}{SetItemText}{\param{const wxDataViewItem\& }{item}, \param{const wxString\& }{text}}

Sets the text of the item.
