\section{\class{wxDocMDIChildFrame}}\label{wxdocmdichildframe}

The wxDocMDIChildFrame class provides a default frame for displaying documents
on separate windows. This class can only be used for MDI child frames.

The class is part of the document/view framework supported by wxWidgets,
and cooperates with the \helpref{wxView}{wxview}, \helpref{wxDocument}{wxdocument},
\rtfsp\helpref{wxDocManager}{wxdocmanager} and \helpref{wxDocTemplate}{wxdoctemplate} classes.

See the example application in {\tt samples/docview}.

\wxheading{Derived from}

\helpref{wxMDIChildFrame}{wxmdichildframe}\\
\helpref{wxFrame}{wxframe}\\
\helpref{wxWindow}{wxwindow}\\
\helpref{wxEvtHandler}{wxevthandler}\\
\helpref{wxObject}{wxobject}

\wxheading{Include files}

<wx/docmdi.h>

\wxheading{See also}

\helpref{Document/view overview}{docviewoverview}, \helpref{wxMDIChildFrame}{wxmdichildframe}

\membersection{wxDocMDIChildFrame::m\_childDocument}\label{wxdocmdichildframemchilddocument}

\member{wxDocument*}{m\_childDocument}

The document associated with the frame.

\membersection{wxDocMDIChildFrame::m\_childView}\label{wxdocmdichildframemchildview}

\member{wxView*}{m\_childView}

The view associated with the frame.

\membersection{wxDocMDIChildFrame::wxDocMDIChildFrame}\label{wxdocmdichildframector}

\func{}{wxDocMDIChildFrame}{\param{wxDocument* }{doc}, \param{wxView* }{view}, \param{wxFrame* }{parent},
 \param{wxWindowID}{ id}, \param{const wxString\& }{title}, \param{const wxPoint\&}{ pos = wxDefaultPosition},
 \param{const wxSize\&}{ size = wxDefaultSize},
 \param{long}{ style = wxDEFAULT\_FRAME\_STYLE}, \param{const wxString\& }{name = ``frame"}}

Constructor.

\membersection{wxDocMDIChildFrame::\destruct{wxDocMDIChildFrame}}\label{wxdocmdichildframedtor}

\func{}{\destruct{wxDocMDIChildFrame}}{\void}

Destructor.

\membersection{wxDocMDIChildFrame::GetDocument}\label{wxdocmdichildframegetdocument}

\constfunc{wxDocument*}{GetDocument}{\void}

Returns the document associated with this frame.

\membersection{wxDocMDIChildFrame::GetView}\label{wxdocmdichildframegetview}

\constfunc{wxView*}{GetView}{\void}

Returns the view associated with this frame.

\membersection{wxDocMDIChildFrame::OnActivate}\label{wxdocmdichildframeonactivate}

\func{void}{OnActivate}{\param{wxActivateEvent}{ event}}

Sets the currently active view to be the frame's view. You may need
to override (but still call) this function in order to set the keyboard
focus for your subwindow.

\membersection{wxDocMDIChildFrame::OnCloseWindow}\label{wxdocmdichildframeonclosewindow}

\func{void}{OnCloseWindow}{\param{wxCloseEvent\&}{ event}}

Closes and deletes the current view and document.

\membersection{wxDocMDIChildFrame::SetDocument}\label{wxdocmdichildframesetdocument}

\func{void}{SetDocument}{\param{wxDocument *}{doc}}

Sets the document for this frame.

\membersection{wxDocMDIChildFrame::SetView}\label{wxdocmdichildframesetview}

\func{void}{SetView}{\param{wxView *}{view}}

Sets the view for this frame.


