\chapter{Libraries list}\label{librarieslist}
\setheader{{\it CHAPTER \thechapter}}{}{}{}{}{{\it CHAPTER \thechapter}}%
\setfooter{\thepage}{}{}{}{}{\thepage}%

Starting from version 2.5.0 wxWindows can be built either as a single large
library (this is called the {\it monolithic build}) or as several smaller
libraries ({\it multilib build}). Multilib build is the default.

wxWindows library is divided into following libraries:

{\large {\bf wxBase}}

Every wxWindows application must link against this library. It contains
mandatory classes that any wxWindows code depends on (e.g.
\helpref{wxString}{wxstring}) and portability classes that abstract
differences between platforms. wxBase can be used to develop console mode
applications, it does not require any GUI libraries or running X Window System
on Unix.

{\large {\bf wxNet}}

Classes for network access:
wxSocket classes (\helpref{wxSocketClient}{wxsocketclient},
\helpref{wxSocketServer}{wxsocketserver} and related classes),
\helpref{wxSocketOutputStream}{wxsocketoutputstream},
\helpref{wxSocketInputStream}{wxsocketinputstream},
sockets-based IPC classes (\helpref{wxTCPServer}{wxddeserver},
\helpref{wxTCPClient}{wxddeclient} and
\helpref{wxTCPConnection}{wxddeconnection}),
\helpref{wxURL}{wxurl},
wxInternetFSHandler (a \helpref{wxFileSystem handler}{fs}).
Requires wxBase.

{\large {\bf wxXML}}

This library contains simple classes for parsing XML documents. Note that
their API {\em will} change in the future and backward
compatibility will not be preserved. Use of this library in your applications
is not recommended, it is only meant for use by XML resources system. Future
versions of wxWindows will contain new XML handling classes with DOM-like API.
Requires wxBase.

{\large {\bf wxODBC}}

\helpref{Database classes}{odbcoverview}. Requires wxBase.

{\large {\bf wxCore}}

Basic GUI classes such as GDI classes or controls are in this library. All
wxWindows GUI applications must link against this library, only console mode
applications don't.

{\large {\bf wxAdvanced}}

More advanced or rarely used GUI classes are in this library.
Requires wxCore and wxBase.

{\large {\bf wxGL}}

This library contains \helpref{wxGLCanvas}{wxglcanvas} class for integrating
OpenGL library with wxWindows. Unlike all other, this library is {\em not}
part of the monolithic library, it is always built as separate library.
Requires wxCore and wxBase.

{\large {\bf wxHTML}}

Simple HTML renderer and other \helpref{HTML rendering classes}{wxhtml} are
contained in this library, as well as
\helpref{wxHtmlHelpController}{wxhtmlhelpcontroller},
\helpref{wxBestHelpController}{wxhelpcontroller} and
\helpref{wxHtmlListBox}{wxhtmllistbox}. Requires wxCore and wxBase.
