%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Name:        listbook.tex
%% Purpose:     wxListbook documentation
%% Author:      Vadim Zeitlin
%% Modified by:
%% Created:     22.08.03
%% RCS-ID:      $Id$
%% Copyright:   (c) 2003 Vadim Zeitlin <vadim@wxwindows.org>
%% License:     wxWindows license
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{\class{wxListbook}}\label{wxlistbook}

wxListbook is a class similar to \helpref{wxNotebook}{wxnotebook} but which
uses a \helpref{wxListCtrl}{wxlistctrl} to show the labels instead of the
tabs.

There is no documentation for this class yet but its usage is
identical to wxNotebook (except for the features clearly related to tabs
only), so please refer to that class documentation for now. You can also
use the \helpref{notebook sample}{samplenotebook} to see wxListbook in action.

\wxheading{Derived from}

wxBookCtrlBase (see \helpref{wxBookCtrl overview}{wxbookctrloverview})\\
\helpref{wxControl}{wxcontrol}\\
\helpref{wxWindow}{wxwindow}\\
\helpref{wxEvtHandler}{wxevthandler}\\
\helpref{wxObject}{wxobject}

\wxheading{Include files}

<wx/listbook.h>

\wxheading{Window styles}

\twocolwidtha{5cm}
\begin{twocollist}\itemsep=0pt

\twocolitem{\windowstyle{wxLB\_DEFAULT}}{Choose the default location for the
labels depending on the current platform (left everywhere except Mac where
it is top).}
\twocolitem{\windowstyle{wxLB\_TOP}}{Place labels above the page area.}
\twocolitem{\windowstyle{wxLB\_LEFT}}{Place labels on the left side.}
\twocolitem{\windowstyle{wxLB\_RIGHT}}{Place labels on the right side.}
\twocolitem{\windowstyle{wxLB\_BOTTOM}}{Place labels below the page area.}

\end{twocollist}

\wxheading{See also}

\helpref{wxBookCtrl}{wxbookctrloverview}, \helpref{wxNotebook}{wxnotebook}, \helpref{notebook sample}{samplenotebook}

