\section{\class{wxPropertyListView}}\label{wxpropertylistview}

\overview{wxPropertyListView overview}{wxpropertylistviewoverview}

The {\bf wxPropertyListView} class shows a wxPropertySheet as a Visual Basic-style property list.

\membersection{wxPropertyListView::wxPropertyListView}

\func{void}{wxPropertyListView}{\param{long}{ flags = wxPROP\_BUTTON\_DEFAULT}}

Constructor.

The {\it flags} argument can be a bit list of the following:

\begin{itemize}\itemsep=0pt
\item wxPROP\_BUTTON\_CLOSE
\item wxPROP\_BUTTON\_OK
\item wxPROP\_BUTTON\_CANCEL
\item wxPROP\_BUTTON\_CHECK\_CROSS
\item wxPROP\_BUTTON\_HELP
\item wxPROP\_DYNAMIC\_VALUE\_FIELD
\item wxPROP\_PULLDOWN
\end{itemize}

\membersection{wxPropertyListView::\destruct{wxPropertyListView}}

\func{void}{\destruct{wxPropertyListView}}{\void}

Destructor.

\membersection{wxPropertyListView::AssociatePanel}\label{wxpropertylistviewassociatepanel}

\func{void}{AssociatePanel}{\param{wxPanel *}{panel}}

Associates the window on which the controls will be displayed, with the view (sets an internal pointer to the window).

\membersection{wxPropertyListView::BeginShowingProperty}\label{wxpropertylistviewbeginshowingproperty}

\func{Bool}{BeginShowingProperty}{\param{wxProperty *}{property}}

Finds the appropriate validator and loads the property into the controls, by calling
wxPropertyValidator::OnPrepareControls and then wxPropertyListView::DisplayProperty.

\membersection{wxPropertyListView::DisplayProperty}\label{wxpropertylistviewdisplayproperty}

\func{Bool}{DisplayProperty}{\param{wxProperty *}{property}}

Calls wxPropertyValidator::OnDisplayValue for the current property's validator. This function
gets called by wxPropertyListView::BeginShowingProperty, which is in turn called
from ShowProperty, called by OnPropertySelect, called by the listbox callback when selected.

\membersection{wxPropertyListView::EndShowingProperty}\label{wxpropertylistviewendshowingproperty}

\func{Bool}{EndShowingProperty}{\param{wxProperty *}{property}}

Finds the appropriate validator and unloads the property from the controls, by calling
wxPropertyListView::RetrieveProperty, wxPropertyValidator::OnClearControls and (if we're in
detailed editing mdoe) wxPropertyValidator::OnClearDetailControls.

\membersection{wxPropertyListView::GetPanel}\label{wxpropertylistviewgetpanel}

\func{wxPanel *}{GetPanel}{\void}

Returns the panel associated with the view.

\membersection{wxPropertyListView::GetManagedWindow}\label{wxpropertylistviewgetmanagedwindow}

\func{wxWindow *}{GetManagedWindow}{\void}

Returns the managed window (a frame or dialog) associated with the view.

\membersection{wxPropertyListView::GetWindowCancelButton}\label{wxpropertylistviewgetwindowcancelbutton}

\func{wxButton *}{GetWindowCancelButton}{\void}

Returns the window cancel button, if any.

\membersection{wxPropertyListView::GetWindowCloseButton}\label{wxpropertylistviewgetwindowclosebutton}

\func{wxButton *}{GetWindowCloseButton}{\void}

Returns the window close or OK button, if any.

\membersection{wxPropertyListView::GetWindowHelpButton}\label{wxpropertylistviewgetwindowhelpbutton}

\func{wxButton *}{GetWindowHelpButton}{\void}

Returns the window help button, if any.

\membersection{wxPropertyListView::SetManagedWindow}\label{wxpropertylistviewsetmanagedwindow}

\func{void}{SetManagedWindow}{\param{wxWindow *}{win}}

Sets the managed window (a frame or dialog) associated with the view.

\membersection{wxPropertyListView::UpdatePropertyDisplayInList}\label{wxpropertylistviewupdatepropdisplay}

\func{Bool}{UpdatePropertyDisplayInList}{\param{wxProperty *}{property}}

Updates the display for the given changed property.

\membersection{wxPropertyListView::UpdatePropertyList}\label{wxpropertylistviewupdateproplist}

\func{Bool}{UpdatePropertyList}{\param{Bool }{clearEditArea = TRUE}}

Updates the whole property list display.


