\section{\class{wxStdDialogButtonSizer}}\label{wxstddialogbuttonsizer}

This class creates button layouts which conform to the standard button spacing and ordering defined by the platform or toolkit's user interface guidelines (if such things exist). By using this class, you can ensure that all your standard dialogs look correct on all major platforms. Currently it conforms to the Windows, GTK and Mac OS X human interface guidelines.

When there aren't interface guidelines defined for a particular platform or toolkit, wxStdDialogButtonSizer reverts to the Windows implementation. 

TO USE THIS CLASS: First, add buttons to the sizer by calling AddButton (or SetAffirmativeButton, SetNegativeButton, or SetCancelButton) and then call Finalise in order to create the actual button layout used. Other than these special operations, this sizer works like any other sizer. 

ALSO NOTE: If you add a button with wxID_SAVE, on Mac OS X the button will be renamed to "Save" and the wxID_NO button will be renamed to "Don't Save" in accordance with the Mac OS X Human Interface Guidelines.

\wxheading{Derived from}

\helpref{wxBoxSizer}{wxboxsizer}\\
\helpref{wxSizer}{wxsizer}\\
\helpref{wxObject}{wxobject}

\wxheading{Include files}

<wx/sizer.h>

\wxheading{See also}

\helpref{wxSizer}{wxsizer}, \helpref{Sizer overview}{sizeroverview}

\func{}{wxStdDialogButtonSizer}{\void}

Constructor for a wxStdDialogButtonSizer.

\membersection{wxStdDialogButtonSizer::AddButton}\label{wxstddialogbuttonsizeraddbutton}

\func{void}{AddButton}{\param{wxButton* }{button}}

Adds a button to the wxStdDialogButtonSizer. The button must have one of the following IDs:

\begin{itemize}
	\item wxID_OK
	\item wxID_YES
	\item wxID_SAVE
	\item wxID_APPLY
	\item wxID_NO
	\item wxID_CANCEL
	\item wxID_HELP
	\item wxID_CONTEXT_HELP
\end{itemize}

\membersection{wxStdDialogButtonSizer::Finalise}\label{wxstddialogbuttonsizerfinalise}

\func{void}{Finalise}{\void}

Rearranges the buttons and applies proper spacing between buttons to make them match the platform or toolkit's interface guidelines.

\membersection{wxStdDialogButtonSizer::SetAffirmativeButton}\label{wxstddialogbuttonsizersetaffirmativebutton}

\func{void}{SetAffirmativeButton}{\param{wxButton* }{button}}

Sets the affirmative button for the sizer. This allows you to use IDs other than the standard IDs outlined above.

\membersection{wxStdDialogButtonSizer::SetCancelButton}\label{wxstddialogbuttonsizersetcancelbutton}

\func{void}{SetCancelButton}{\param{wxButton* }{button}}

Sets the cancel button for the sizer. This allows you to use IDs other than the standard IDs outlined above.

\membersection{wxStdDialogButtonSizer::SetNegativeButton}\label{wxstddialogbuttonsizersetnegativebutton}

\func{void}{SetNegativeButton}{\param{wxButton* }{button}}

Sets the negative button for the sizer. This allows you to use IDs other than the standard IDs outlined above.
