%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Name:        wxusedef.tex
%% Purpose:     wxUSE preprocessor symbols
%% Author:      Tim Stahlhut
%% Created:     2007-07-15
%% RCS-ID:      $Id: $
%% Copyright:   (c) 2007 wxWidgets
%% License:     wxWindows license
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{wxUSE Preprocessor symbols defined by wxWidgets}\label{wxusedef}

This section documents the wxUSE preprocessor symbols used in the wxWidgets
source, grouped by category (and sorted by alphabetical order inside each
category). These symbols are always defined and whether the given feature is
active or not depends on their value: if defined as $1$, feature is active,
otherwise it is disabled. Because of this these symbols should be always tested
using \texttt{#if} and not \texttt{#ifdef}.

\subsection{Generic wxUSE preprocessor symbols}\label{wxusedefmulti}

\begin{twocollist}\itemsep=0pt
\twocolitem{wxUSE\_ABOUTDLG}{Use \helpref{wxAboutDialogInfo}{wxaboutdialoginfo} class.}
\twocolitem{wxUSE\_ACCEL}{Use \helpref{wxAcceleratorTable}{wxacceleratortable}/Entry classes and support for them in \helpref{wxMenu}{wxmenu}(Bar).}
\twocolitem{wxUSE\_ANIMATIONCTRL}{Use \helpref{wxAnimationCtrl}{wxanimationctrl} class.}
\twocolitem{wxUSE\_APPLE\_IEEE}{IEEE Extended to/from double routines; see src/common/extended.c file.}
\twocolitem{wxUSE\_ARCHIVE\_STREAMS}{Enable streams for archive formats.}
\twocolitem{wxUSE\_AUI}{Use AUI (dockable windows) library.}
\twocolitem{wxUSE\_BASE64}{Enables Base64 support.}
\twocolitem{wxUSE\_BITMAPCOMBOBOX}{}
\twocolitem{wxUSE\_BMPBUTTON}{Use \helpref{wxBitmapButton}{wxbitmapbutton} class.}
\twocolitem{wxUSE\_BUSYINFO}{Use \helpref{wxBusyInfo}{wxbusyinfo} class.}
\twocolitem{wxUSE\_BUTTON}{Use \helpref{wxButton}{wxbutton} class.}
\twocolitem{wxUSE\_CALENDARCTRL}{Use \helpref{wxCalendarCtrl}{wxcalendarctrl} class.}
\twocolitem{wxUSE\_CARET}{Use \helpref{wxCaret}{wxcaret} class.}
\twocolitem{wxUSE\_CHECKBOX}{Use \helpref{wxCheckBox}{wxcheckbox} class.}
\twocolitem{wxUSE\_CHECKLISTBOX}{Use \helpref{wxCheckListBox}{wxchecklistbox} class.}
\twocolitem{wxUSE\_CHOICE}{Use \helpref{wxChoice}{wxchoice} class.}
\twocolitem{wxUSE\_CHOICEBOOK}{Use \helpref{wxChoicebook}{wxchoicebook} class.}
\twocolitem{wxUSE\_CHOICEDLG}{Use \helpref{wxSingleChoiceDialog}{wxsinglechoicedialog} or \helpref{wxMultiChoiceDialog}{wxmultichoicedialog} classes.}
\twocolitem{wxUSE\_CLIPBOARD}{Use \helpref{wxClipboard}{wxclipboard} class.}
\twocolitem{wxUSE\_CMDLINE\_PARSER}{Use \helpref{wxCmdLineParser}{wxcmdlineparser} class.}
\twocolitem{wxUSE\_COLLPANE}{Use \helpref{wxCollapsiblePane}{wxcollapsiblepane} class.}
\twocolitem{wxUSE\_COLOURDLG}{Use \helpref{wxColourDialog}{wxcolourdialog} class.}
\twocolitem{wxUSE\_COLOURPICKERCTRL}{Use \helpref{wxColourPickerCtrl}{wxcolourpickerctrl} class.}
\twocolitem{wxUSE\_COMBOBOX}{Use \helpref{wxComboBox}{wxcombobox} class.}
\twocolitem{wxUSE\_COMBOCTRL}{Use \helpref{wxComboCtrl}{wxcomboctrl} class.}
\twocolitem{wxUSE\_CONFIG}{Use \helpref{wxConfig}{wxconfigbase} and related classes.}
\twocolitem{wxUSE\_CONFIG\_NATIVE}{When enabled use native OS configuration instead of the \helpref{wxFileConfig}{wxfileconfig} class.}
\twocolitem{wxUSE\_CONSOLE\_EVENTLOOP}{Enable event loop in console programs.}
\twocolitem{wxUSE\_CONSTRAINTS}{Use \helpref{wxLayoutConstraints}{wxlayoutconstraints}}
\twocolitem{wxUSE\_CONTROLS}{If set to $0$, no classes deriving from \helpref{wxControl}{wxcontrol} can be used.}
\twocolitem{wxUSE\_CRASHREPORT}{Use wxCrashReport class.}
\twocolitem{wxUSE\_DATAOBJ}{Use \helpref{wxDataObject}{wxdataobject} and related classes.}
\twocolitem{wxUSE\_DATAVIEWCTRL}{Use \helpref{wxDataViewCtrl}{wxdataviewctrl} class.}
\twocolitem{wxUSE\_DATEPICKCTRL}{Use \helpref{wxDatePickerCtrl}{wxdatepickerctrl} class.}
\twocolitem{wxUSE\_DATETIME}{Use \helpref{wxDateTime}{wxdatetime} and related classes.}
\twocolitem{wxUSE\_DBGHELP}{Use wxDbgHelpDLL class.}
\twocolitem{wxUSE\_DEBUG\_CONTEXT}{Use \helpref{wxDebugContext}{wxdebugcontext} class.}
\twocolitem{wxUSE\_DEBUG\_NEW\_ALWAYS}{See wx/object.h file.}
\twocolitem{wxUSE\_DEBUGREPORT}{Use \helpref{wxDebugReport}{wxdebugreport} class.}
\twocolitem{wxUSE\_DIALUP\_MANAGER}{Use \helpref{wxDialUpManager}{wxdialupmanager} and related classes.}
\twocolitem{wxUSE\_DIRDLG}{Use \helpref{wxDirDialog}{wxdirdialog} class.}
\twocolitem{wxUSE\_DIRPICKERCTRL}{Use \helpref{wxDirPickerCtrl}{wxdirpickerctrl} class.}
\twocolitem{wxUSE\_DISPLAY}{Use \helpref{wxDisplay}{wxdisplay} and related classes.}
\twocolitem{wxUSE\_DOC\_VIEW\_ARCHITECTURE}{Use \helpref{wxDocument}{wxdocument} and related classes.}
\twocolitem{wxUSE\_DRAG\_AND\_DROP}{Use \helpref{Drag and drop}{wxdndoverview} classes.}
\twocolitem{wxUSE\_DRAGIMAGE}{Use \helpref{wxDragImage}{wxdragimage} class.}
\twocolitem{wxUSE\_DYNAMIC\_LOADER}{Use wxPluginManager and related classes. Requires \helpref{wxDynamicLibrary}{wxdynamiclibrary}}
\twocolitem{wxUSE\_DYNLIB\_CLASS}{Use \helpref{wxDynamicLibrary}{wxdynamiclibrary}}
\twocolitem{wxUSE\_EDITABLELISTBOX}{Use \helpref{wxEditableListBox}{wxeditablelistbox} class.}
\twocolitem{wxUSE\_EXCEPTIONS}{}
\twocolitem{wxUSE\_EXPAT}{enable XML support using expat parser.}
\twocolitem{wxUSE\_EXTENDED\_RTTI}{Use extended RTTI, see also \helpref{Runtime class information (RTTI)}{runtimeclassoverview}}
\twocolitem{wxUSE\_FFILE}{Use \helpref{wxFFile}{wxffile} class.}
\twocolitem{wxUSE\_FILE}{Use \helpref{wxFile}{wxfile} class.}
\twocolitem{wxUSE\_FILECONFIG}{Use \helpref{wxFileConfig}{wxfileconfig} class.}
\twocolitem{wxUSE\_FILEDLG}{Use \helpref{wxFileDialog}{wxfiledialog} class.}
\twocolitem{wxUSE\_FONTENUM}{Use \helpref{wxFontEnumerator}{wxfontenumerator} class.}
\twocolitem{wxUSE\_FILEPICKERCTRL}{Use \helpref{wxFilePickerCtrl}{wxfilepickerctrl} class.}
\twocolitem{wxUSE\_FS\_ARCHIVE}{Use virtual archive filesystems like wxArchiveFSHandler in \helpref{wxFileSystem}{wxfilesystem} class.}
\twocolitem{wxUSE\_FS\_INET}{Use virtual HTTP/FTP filesystems like wxInternetFSHandler in \helpref{wxFileSystem}{wxfilesystem} class.}
\twocolitem{wxUSE\_FS\_ZIP}{Please use wxUSE\_FS\_ARCHIVE instead.}
\twocolitem{wxUSE\_FILESYSTEM}{Use \helpref{wxFileSystem}{wxfilesystem} and related classes.}
\twocolitem{wxUSE\_FINDREPLDLG}{Use \helpref{wxFindReplaceDialog}{wxfindreplacedialog} class.}
\twocolitem{wxUSE\_FONTDLG}{Use \helpref{wxFontDialog}{wxfontdialog} class.}
\twocolitem{wxUSE\_FONTMAP}{Use \helpref{wxFontMapper}{wxfontmapper} class.}
\twocolitem{wxUSE\_FONTPICKERCTRL}{Use \helpref{wxFontPickerCtrl}{wxfontpickerctrl} class.}
\twocolitem{wxUSE\_FSVOLUME}{Use wxFSVolume class.}
\twocolitem{wxUSE\_GAUGE}{Use \helpref{wxGauge}{wxgauge} class.}
\twocolitem{wxUSE\_GENERIC\_DRAGIMAGE}{Used in wxDragImage sample.}
\twocolitem{wxUSE\_GENERIC\_DRAWELLIPSE}{See comment in wx/dc.h file.}
\twocolitem{wxUSE\_GEOMETRY}{Use common geometry classes}
\twocolitem{wxUSE\_GIF}{Use GIF \helpref{wxImageHandler}{wximagehandler}}
\twocolitem{wxUSE\_GLCANVAS}{Enables OpenGL support.}
\twocolitem{wxUSE\_GLOBAL\_MEMORY\_OPERATORS}{Override global operators \texttt{new} and \texttt{delete}}
\twocolitem{wxUSE\_GRAPHICS\_CONTEXT}{Use \helpref{wxGraphicsContext}{wxgraphicscontext} and related classes.}
\twocolitem{wxUSE\_GRID}{Use \helpref{wxGrid}{wxgrid} and related classes.}
\twocolitem{wxUSE\_GUI}{Use the GUI classes; if set to $0$ only non-GUI classes are available.}
\twocolitem{wxUSE\_HELP}{Use \helpref{wxHelpController}{wxhelpcontroller} and related classes.}
\twocolitem{wxUSE\_HTML}{Use \helpref{wxHtmlWindow}{wxhtmlwindow} and related classes.}
\twocolitem{wxUSE\_HYPERLINKCTRL}{Use \helpref{wxHyperlinkCtrl}{wxhyperlinkctrl}}
\twocolitem{wxUSE\_ICO\_CUR}{Support Windows ICO and CUR formats.}
\twocolitem{wxUSE\_IFF}{Enables the \helpref{wxImage}{wximage} handler for Amiga IFF images.}
\twocolitem{wxUSE\_IMAGE}{Use \helpref{wxImage}{wximage} and related classes.}
\twocolitem{wxUSE\_IMAGLIST}{Use \helpref{wxImageList}{wximagelist} class.}
\twocolitem{wxUSE\_INTL}{Use \helpref{wxLocale}{wxlocale} and related classes.}
\twocolitem{wxUSE\_IOSTREAMH}{Use header <iostream.h> instead of <iostream>.}
\twocolitem{wxUSE\_IPC}{Use interprocess communication classes.}
\twocolitem{wxUSE\_IPV6}{Use experimental \helpref{wxIPV6address}{wxipaddress} and related classes.}
\twocolitem{wxUSE\_JOYSTICK}{Use \helpref{wxJoystick}{wxjoystick} class.}
\twocolitem{wxUSE\_LIBJPEG}{Enables JPEG format support (requires libjpeg).}
\twocolitem{wxUSE\_LIBPNG}{Enables PNG format support (requires libpng). Also requires wxUSE\_ZLIB.}
\twocolitem{wxUSE\_LIBTIFF}{Enables TIFF format support (requires libtiff).}
\twocolitem{wxUSE\_LISTBOOK}{Use \helpref{wxListbook}{wxlistbook} class.}
\twocolitem{wxUSE\_LISTBOX}{Use \helpref{wxListBox}{wxlistbox} class.}
\twocolitem{wxUSE\_LISTCTRL}{Use \helpref{wxListCtrl}{wxlistctrl} class.}
\twocolitem{wxUSE\_LOG}{Use \helpref{wxLog}{wxlog} and related classes.}
\twocolitem{wxUSE\_LOG\_DEBUG}{Enabled when wxLog used with \_\_WXDEBUG\_\_ defined.}
\twocolitem{wxUSE\_LOG\_DIALOG}{Use wxLogDialog class.}
\twocolitem{wxUSE\_LOGGUI}{Use \helpref{wxLogGui}{wxloggui} class.}
\twocolitem{wxUSE\_LOGWINDOW}{Use wxLogFrame class.}
\twocolitem{wxUSE\_LONGLONG}{Use \helpref{wxLongLong}{wxlonglong} class.}
\twocolitem{wxUSE\_LONGLONG\_NATIVE}{Use native \texttt{long long} type in \helpref{wxLongLong}{wxlonglong} implementation.}
\twocolitem{wxUSE\_LONGLONG\_WX}{Use generic wxLongLong implementation.}
\twocolitem{wxUSE\_MDI}{Use \helpref{wxMDIParentFrame}{wxmdiparentframe} and \helpref{wxMDIChildFrame}{wxmdichildframe}}
\twocolitem{wxUSE\_MDI\_ARCHITECTURE}{Use MDI-based document-view classes.}
\twocolitem{wxUSE\_MEDIACTRL}{Use \helpref{wxMediaCtrl}{wxmediactrl}.}
\twocolitem{wxUSE\_MENUS}{Use \helpref{wxMenu}{wxmenu} and related classes.}
\twocolitem{wxUSE\_METAFILE}{Use \helpref{wxMetaFile}{wxmetafile} and related classes.}
\twocolitem{wxUSE\_MIMETYPE}{Use \helpref{wxFileType}{wxfiletype} class.}
\twocolitem{wxUSE\_MINIFRAME}{Use \helpref{wxMiniFrame}{wxminiframe} class.}
\twocolitem{wxUSE\_MOUSEWHEEL}{Support mouse wheel events.}
\twocolitem{wxUSE\_MSGDLG}{Use wxMessageOutput class.}
\twocolitem{wxUSE\_NOTEBOOK}{Use \helpref{wxNotebook}{wxnotebook} and related classes.}
\twocolitem{wxUSE\_NUMBERDLG}{Use wxNumberEntryDialog class.}
\twocolitem{wxUSE\_ODBC}{Use ODBC classes.}
\twocolitem{wxUSE\_ODCOMBOBOX}{Use \helpref{wxOwnerDrawnComboBox}{wxownerdrawncombobox} class.}
\twocolitem{wxUSE\_ON\_FATAL\_EXCEPTION}{Catch signals in \helpref{wxApp::OnFatalException}{wxapponfatalexception} method.}
\twocolitem{wxUSE\_OPENGL}{Please use wxUSE\_GLCANVAS to test for enabled OpenGL support instead.}
\twocolitem{wxUSE\_OWNER\_DRAWN}{Use interface for owner-drawn GUI elements.}
\twocolitem{wxUSE\_PALETTE}{Use \helpref{wxPalette}{wxpalette} and related classes.}
\twocolitem{wxUSE\_PCX}{Enables \helpref{wxImage}{wximage} PCX handler.}
\twocolitem{wxUSE\_PNM}{Enables \helpref{wxImage}{wximage} PNM handler.}
\twocolitem{wxUSE\_POPUPWIN}{Use wxPopupWindow class.}
\twocolitem{wxUSE\_POSTSCRIPT}{Use wxPostScriptPrinter class.}
\twocolitem{wxUSE\_PRINTF\_POS\_PARAMS}{Use \helpref{wxVsnprintf}{wxvsnprintf} which supports positional parameters.}
\twocolitem{wxUSE\_PRINTING\_ARCHITECTURE}{Enable printer classes.}
\twocolitem{wxUSE\_PROGRESSDLG}{Enables progress dialog classes.}
\twocolitem{wxUSE\_PROTOCOL}{Use \helpref{wxProtocol}{wxprotocol} and derived classes.}
\twocolitem{wxUSE\_PROTOCOL\_FILE}{Use wxFileProto class. (requires \helpref{wxProtocol}{wxprotocol})}
\twocolitem{wxUSE\_PROTOCOL\_FTP}{Use \helpref{wxFTP}{wxftp} class. (requires \helpref{wxProtocol}{wxprotocol})}
\twocolitem{wxUSE\_PROTOCOL\_HTTP}{Use \helpref{wxHTTP}{wxhttp} class. (requires \helpref{wxProtocol}{wxprotocol})}
\twocolitem{wxUSE\_RADIOBOX}{Use \helpref{wxRadioBox}{wxradiobox} class.}
\twocolitem{wxUSE\_RADIOBTN}{Use \helpref{wxRadioButton}{wxradiobutton} class.}
\twocolitem{wxUSE\_REGEX}{Use \helpref{wxRegEx}{wxregex} class.}
\twocolitem{wxUSE\_RICHTEXT}{Use \helpref{wxRichTextCtrl}{wxrichtextctrl} class.}
\twocolitem{wxUSE\_RICHTEXT\_XML\_HANDLER}{See src/xrc/xh\_richtext.cpp file.}
\twocolitem{wxUSE\_SASH}{Use \helpref{wxSashWindow}{wxsashwindow} class.}
\twocolitem{wxUSE\_SCROLLBAR}{Use \helpref{wxScrollBar}{wxscrollbar} class.}
\twocolitem{wxUSE\_SEARCHCTRL}{Use \helpref{wxSearchCtrl}{wxsearchctrl} class.}
\twocolitem{wxUSE\_SELECT\_DISPATCHER}{Use wxSelectDispatcher class.}
\twocolitem{wxUSE\_SLIDER}{Use \helpref{wxSlider}{wxslider} class.}
\twocolitem{wxUSE\_SNGLINST\_CHECKER}{Use \helpref{wxSingleInstanceChecker}{wxsingleinstancechecker} class.}
\twocolitem{wxUSE\_SOCKETS}{Enables Network address classes.}
\twocolitem{wxUSE\_SOUND}{Use \helpref{wxSound}{wxsound} class.}
\twocolitem{wxUSE\_SPINBTN}{Use \helpref{wxSpinButton}{wxspinbutton} class.}
\twocolitem{wxUSE\_SPINCTRL}{Use \helpref{wxSpinCtrl}{wxspinctrl} class.}
\twocolitem{wxUSE\_SPLASH}{Use \helpref{wxSplashScreen}{wxsplashscreen} class.}
\twocolitem{wxUSE\_SPLINES}{Provide methods for spline drawing in wxDC.}
\twocolitem{wxUSE\_SPLITTER}{Use \helpref{wxSplitterWindow}{wxsplitterwindow} class.}
\twocolitem{wxUSE\_STACKWALKER}{Enables \helpref{wxStackWalker}{wxstackwalker} and related classes.}
\twocolitem{wxUSE\_STARTUP\_TIPS}{Use startup tips, \helpref{wxTipProvider}{wxtipprovider} class.}
\twocolitem{wxUSE\_STATBMP}{Use \helpref{wxStaticBitmap}{wxstaticbitmap} class.}
\twocolitem{wxUSE\_STATBOX}{Use \helpref{wxStaticBox}{wxstaticbox} class.}
\twocolitem{wxUSE\_STATLINE}{Use \helpref{wxStaticLine}{wxstaticline} class.}
\twocolitem{wxUSE\_STATTEXT}{Use \helpref{wxStaticText}{wxstatictext} class.}
\twocolitem{wxUSE\_STATUSBAR}{Use \helpref{wxStatusBar}{wxstatusbar} class.}
\twocolitem{wxUSE\_STC}{Use wxStyledTextCtrl.}
\twocolitem{wxUSE\_STD\_IOSTREAM}{Use standard C++ stream classes.}
\twocolitem{wxUSE\_STD\_STRING}{Use standard C++ string classes.}
\twocolitem{wxUSE\_STDPATHS}{Use \helpref{wxStandardPaths}{wxstandardpaths} class.}
\twocolitem{wxUSE\_STL}{Use Standard Template Library for the container classes and \helpref{wxString}{wxstring} implementation.}
\twocolitem{wxUSE\_STOPWATCH}{Use \helpref{wxStopWatch}{wxstopwatch} class.}
\twocolitem{wxUSE\_STREAMS}{Enable stream classes.}
\twocolitem{wxUSE\_SVG}{Use wxSVGFileDC class.}
\twocolitem{wxUSE\_SYSTEM\_OPTIONS}{Use \helpref{wxSystemOptions}{wxsystemoptions} class.}
\twocolitem{wxUSE\_TAB\_DIALOG}{Use \helpref{wxTabControl}{wxtabcontrol} class.}
\twocolitem{wxUSE\_TARSTREAM}{Enable Tar files support.}
\twocolitem{wxUSE\_TASKBARICON}{Use \helpref{wxTaskBarIcon}{wxtaskbaricon} class.}
\twocolitem{wxUSE\_TEXTBUFFER}{Use wxTextBuffer class.}
\twocolitem{wxUSE\_TEXTCTRL}{Use \helpref{wxTextCtrl}{wxtextctrl} class.}
\twocolitem{wxUSE\_TEXTDLG}{Use \helpref{wxTextEntryDialog}{wxtextentrydialog} class.}
\twocolitem{wxUSE\_TEXTFILE}{Use \helpref{wxTextFile}{wxtextfile} class.}
\twocolitem{wxUSE\_TGA}{Enable \helpref{wxImage}{wximage} TGA handler.}
\twocolitem{wxUSE\_THREADS}{Use \helpref{wxThread}{wxthread} and related classes.}
\twocolitem{wxUSE\_TIMER}{Use \helpref{wxTimer}{wxtimer} class.}
\twocolitem{wxUSE\_TIPWINDOW}{Use \helpref{wxTipWindow}{wxtipwindow} class.}
\twocolitem{wxUSE\_TOGGLEBTN}{Use \helpref{wxToggleButton}{wxtogglebutton} class.}
\twocolitem{wxUSE\_TOOLBAR}{Use \helpref{wxToolBar}{wxtoolbar} class.}
\twocolitem{wxUSE\_TOOLBOOK}{Use \helpref{wxToolbook}{wxtoolbook} class.}
\twocolitem{wxUSE\_TOOLTIPS}{Use \helpref{wxToolTip}{wxtooltip} class.}
\twocolitem{wxUSE\_TREEBOOK}{Use \helpref{wxTreebook}{wxtreebook} class.}
\twocolitem{wxUSE\_TREECTRL}{Use \helpref{wxTreeCtrl}{wxtreectrl} class.}
\twocolitem{wxUSE\_TTM\_WINDOWFROMPOINT}{Obsolete, do not use.}
\twocolitem{wxUSE\_UNICODE}{Compiled with Unicode support.}
\twocolitem{wxUSE\_UNICODE\_UTF8}{Compiled with UTF8 support.}
\twocolitem{wxUSE\_UNICODE\_WCHAR}{Compiled with Unicode support and using wchar\_t type.}
\twocolitem{wxUSE\_URL}{Use \helpref{wxURL}{wxurl} class.}
\twocolitem{wxUSE\_URL\_NATIVE}{Use native support for some operations with \helpref{wxURL}{wxurl}.}
\twocolitem{wxUSE\_UTF8\_LOCALE\_ONLY}{Build wxWidgets to support running only under UTF-8 (and C) locale. This eliminates the code necessary for conversions from the other locales and reduces the library size; useful for embedded systems.}
\twocolitem{wxUSE\_VALIDATORS}{Use \helpref{wxValidator}{wxvalidator} class.}
\twocolitem{wxUSE\_VARIANT}{Use \helpref{wxVariant}{wxvariant} class.}
\twocolitem{wxUSE\_WIZARDDLG}{Use \helpref{wxWizard}{wxwizard} class.}
\twocolitem{wxUSE\_WXHTML\_HELP}{Use \helpref{wxHtmlHelpController}{wxhtmlhelpcontroller} and related classes.}
\twocolitem{wxUSE\_XML}{Use XML parsing classes.}
\twocolitem{wxUSE\_XPM}{Enable XPM reader for \helpref{wxImage}{wximage} and \helpref{wxBitmap}{wxbitmap} classes.}
\twocolitem{wxUSE\_XRC}{Use XRC XML-based resource system.}
\twocolitem{wxUSE\_ZIPSTREAM}{Enable streams for Zip files.}
\twocolitem{wxUSE\_ZLIB}{Use \helpref{wxZlibInput}{wxzlibinputstream} and \helpref{wxZlibOutputStream}{wxzliboutputstream} classes, required by wxUSE\_LIBPNG.}
\end{twocollist}

\subsection{wxUSE preprocessor symbols used only under Unix platforms}\label{wxusedefunix}
\begin{twocollist}\itemsep=0pt
\twocolitem{wxUSE\_EPOLL\_DISPATCHER}{Use wxEpollDispatcher class. See also wxUSE\_SELECT\_DISPATCHER.}
\twocolitem{wxUSE\_GSTREAMER}{Use GStreamer library in \helpref{wxMediaCtrl}{wxmediactrl}.}
\twocolitem{wxUSE\_LIBMSPACK}{Use libmspack library.}
\twocolitem{wxUSE\_LIBSDL}{Use SDL for wxSound implementation.}
\twocolitem{wxUSE\_PLUGINS}{See also wxUSE\_LIBSDL.}
\twocolitem{wxUSE\_UNIX}{Enabled on Unix Platform.}
\end{twocollist}

\subsection{wxUSE preprocessor symbols used only in wxX11 Platform}\label{wxusedefx11}
\begin{twocollist}\itemsep=0pt
\twocolitem{wxUSE\_NANOX}{Use NanoX.}
\twocolitem{wxUSE\_UNIV\_TEXTCTRL}{Use wxUniv's implementation of \helpref{wxTextCtrl}{wxtextctrl} class.}
\end{twocollist}

\subsection{wxUSE preprocessor symbols used only in wxGTK port}\label{wxusedefgtk}
\begin{twocollist}\itemsep=0pt
\twocolitem{wxUSE\_DETECT\_SM}{Use code to detect X11 session manager.}
\twocolitem{wxUSE\_LIBGNOMEPRINT}{Use GNOME printing support.}
\twocolitem{wxUSE\_LIBGNOMEVFS}{Use GNOME VFS support.}
\twocolitem{wxUSE\_LIBGNOMEVS}{Use GNOME VFS support.}
\twocolitem{wxUSE\_LIBHILDON}{Use Hildon framework for Nokia 770. Note, does not seem to do anything.}
\end{twocollist}

\subsection{wxUSE preprocessor symbols used only in wxMac port}\label{wxusedefmac}
\begin{twocollist}\itemsep=0pt
\twocolitem{wxUSE\_MAC\_CRITICAL\_REGION\_MUTEX}{See src/mac/carbon/thread.cpp file.}
\twocolitem{wxUSE\_MAC\_PTHREADS\_MUTEX}{See src/mac/carbon/thread.cpp file.}
\twocolitem{wxUSE\_MAC\_SEMAPHORE\_MUTEX}{See src/mac/carbon/thread.cpp file.}
\twocolitem{wxUSE\_WEBKIT}{Use wxWebKitCtrl class.}
\end{twocollist}

\subsection{wxUSE preprocessor symbols used only in wxMotif port}\label{wxusedefmotif}
\begin{twocollist}\itemsep=0pt
\twocolitem{wxUSE\_GADGETS}{Use xmCascadeButtonGadgetClass, xmLabelGadgetClass, xmPushButtonGadgetClass and xmToggleButtonGadgetClass classes.}
\twocolitem{wxUSE\_INVISIBLE\_RESIZE}{See src/motif/dialog.cpp file.}
\end{twocollist}

\subsection{wxUSE preprocessor symbols used only in Cocoa port}
\begin{twocollist}\itemsep=0pt
\twocolitem{wxUSE\_OBJC\_UNIQUIFYING}{Enable Objective-C class name uniquifying.}
\end{twocollist}

\subsection{wxUSE preprocessor symbols used only in OS2 port}
\begin{twocollist}\itemsep=0pt
\twocolitem{wxUSE\_CONSOLEDEBUG}{See src/os2/app.cpp file.}
\twocolitem{wxUSE\_DDE}{See src/os2/mimetype.cpp file.}
\twocolitem{wxUSE\_IMAGE\_LOADING\_IN\_MSW}{See src/os2/clipbrd.cpp file.}
\twocolitem{wxUSE\_IMAGE\_LOADING\_IN\_OS2}{See src/os2/gdiimage.cpp file.}
\twocolitem{wxUSE\_NET\_API}{Use NetBios32GetInfo API call.}
\twocolitem{wxUSE\_RESOURCE\_LOADING\_IN\_OS2}{See src/os2/gdiimage.cpp file.}
\end{twocollist}

\subsection{wxUSE preprocessor symbols used only in wxMSW port}\label{wxusedefmsw}
\begin{twocollist}\itemsep=0pt
\twocolitem{wxUSE\_ACCESSIBILITY}{Enable accessibility support}
\twocolitem{wxUSE\_ACTIVEX}{Use \helpref{wxActiveXContainer}{wxactivexcontainer} and related classes.}
\twocolitem{wxUSE\_COMBOCTRL\_POPUP\_ANIMATION}{See wx/msw/combo.h file.}
\twocolitem{wxUSE\_COMCTL32\_SAFELY}{See src/msw/treectrl.cpp file.}
\twocolitem{wxUSE\_COMMON\_DIALOGS}{Enable use of windows common dialogs from header commdlg.h; example PRINTDLG.}
\twocolitem{wxUSE\_DATEPICKCTRL\_GENERIC}{Use generic \helpref{wxDatePickerCtrl}{wxdatepickerctrl} implementation in addition to the native one.}
\twocolitem{wxUSE\_DC\_CACHEING}{cache temporary \helpref{wxDC}{wxdc} objects.}
\twocolitem{wxUSE\_DIRECTDRAW}{Enable use of the system include file ddraw.h.}
\twocolitem{wxUSE\_DDE\_FOR\_IPC}{See wx/ipc.h file.}
\twocolitem{wxUSE\_ENH\_METAFILE}{Use wxEnhMetaFile.}
\twocolitem{wxUSE\_HOTKEY}{Use \helpref{wxWindow::RegisterHotKey()}{wxwindowregisterhotkey} and \helpref{UnregisterHotKey}{wxwindowunregisterhotkey}}
\twocolitem{wxUSE\_INKEDIT}{Use InkEdit library. Related to Tablet PCs.}
\twocolitem{wxUSE\_MS\_HTML\_HELP}{Use \helpref{wxCHMHelpController}{wxhelpcontroller} class.}
\twocolitem{wxUSE\_NO\_MANIFEST}{Use to prevent the auto generation, under MSVC, of manifest file needed by windows XP and above.}
\twocolitem{wxUSE\_NORLANDER\_HEADERS}{Using headers whose author is Anders Norlander.}
\twocolitem{wxUSE\_OLE}{Enables OLE helper routines.}
\twocolitem{wxUSE\_OLE\_AUTOMATION}{Enable OLE automation utilities.}
\twocolitem{wxUSE\_OLE\_CLIPBOARD}{Use OLE clipboard.}
\twocolitem{wxUSE\_PENWINDOWS}{See src/msw/penwin.cpp file.}
\twocolitem{wxUSE\_POSTSCRIPT\_ARCHITECTURE\_IN\_MSW}{Use PS printing in wxMSW.}
\twocolitem{wxUSE\_PS\_PRINTING}{See src/msw/dcprint.cpp file.}
\twocolitem{wxUSE\_REGKEY}{Use \helpref{wxRegKey}{wxregkey} class.}
\twocolitem{wxUSE\_RICHEDIT}{Enable use of riched32.dll in \helpref{wxTextCtrl}{wxtextctrl}}
\twocolitem{wxUSE\_RICHEDIT2}{Enable use of riched20.dll in \helpref{wxTextCtrl}{wxtextctrl}}
\twocolitem{wxUSE\_VC\_CRTDBG}{See wx/msw/msvcrt.h file.}
\twocolitem{wxUSE\_UNICODE\_MSLU}{Use MSLU for Unicode support under Windows 9x systems.}
\twocolitem{wxUSE\_UXTHEME}{Enable support for XP themes.}
\twocolitem{wxUSE\_WIN\_METAFILES\_ALWAYS}{Use \helpref{wxMetaFile}{wxmetafile} even when wxUSE\_ENH\_METAFILE=$1$.}
\twocolitem{wxUSE\_WXDIB}{Use wxDIB class.}
\twocolitem{wxUSE\_XPM\_IN\_MSW}{See also wxUSE\_XPM}
\end{twocollist}

\subsection{wxUSE preprocessor symbols used only in wxUniversal}\label{wxusedefuniv}
\begin{twocollist}\itemsep=0pt
\twocolitem{wxUSE\_ALL\_THEMES}{Use all themes in wxUniversal; See wx/univ/theme.h file.}
\twocolitem{wxUSE\_THEME\_GTK}{Use GTK+ 1-like theme in wxUniversal}
\twocolitem{wxUSE\_THEME\_METAL}{Use GTK+ 2-like theme in wxUniversal}
\twocolitem{wxUSE\_THEME\_MONO}{Use simple monochrome theme in wxUniversal}
\twocolitem{wxUSE\_THEME\_WIN32}{Use Win32-like theme in wxUniversal}
\end{twocollist}
