
\section{\class{wxDataViewColumn}}\label{wxdataviewcolumn}


This class represents a column in a \helpref{wxDataViewCtrl}{wxdataviewctrl}.
One wxDataViewColumn is bound to one column in the data model,
to which the wxDataViewCtrl has been associated. 

An instance of \helpref{wxDataViewRenderer}{wxdataviewrenderer} is used by
this class to render its data.

\wxheading{Constants}

These flags define behavi

{\small
\begin{verbatim}
enum wxDataViewColumnFlags
{
    wxDATAVIEW_COL_RESIZABLE  = 1,    // the user can resize the column
    wxDATAVIEW_COL_SORTABLE   = 2,    // same as SetSortable()
    wxDATAVIEW_COL_HIDDEN     = 4     // column is hidden
};
\end{verbatim}
}

\wxheading{Derived from}

\helpref{wxObject}{wxobject}

\wxheading{Include files}

<wx/dataview.h>


\membersection{wxDataViewColumn::wxDataViewColumn}\label{wxdataviewcolumnwxdataviewcolumn}

\func{}{wxDataViewColumn}{\param{const wxString\& }{title}, \param{wxDataViewRenderer* }{renderer}, \param{unsigned int }{model\_column}, \param{int }{width = 80}, \param{int }{flags = wxDATAVIEW\_COL\_RESIZABLE}}


\func{}{wxDataViewColumn}{\param{const wxBitmap\& }{bitmap}, \param{wxDataViewRenderer* }{renderer}, \param{unsigned int }{model\_column}, \param{int }{width = 80}, \param{int }{flags = wxDATAVIEW\_COL\_RESIZABLE}}

Constructors.


\membersection{wxDataViewColumn::\destruct{wxDataViewColumn}}\label{wxdataviewcolumndtor}

\func{}{\destruct{wxDataViewColumn}}{\void}

Destructor.

\membersection{wxDataViewColumn::GetBitmap}\label{wxdataviewcolumngetbitmap}

\func{const wxBitmap\&}{GetBitmap}{\void}

Returns the bitmap in the header of the column, if any.

\membersection{wxDataViewColumn::GetModelColumn}\label{wxdataviewcolumngetmodelcolumn}

\func{unsigned int}{GetModelColumn}{\void}

Returns the index of the column of the model, which this
wxDataViewColumn is displaying.

\membersection{wxDataViewColumn::GetOwner}\label{wxdataviewcolumngetowner}

\func{wxDataViewCtrl*}{GetOwner}{\void}

Returns the owning \helpref{wxDataViewCtrl}{wxdataviewctrl}.

\membersection{wxDataViewColumn::GetRenderer}\label{wxdataviewcolumngetrenderer}

\func{wxDataViewRenderer*}{GetRenderer}{\void}

Returns the renderer of this wxDataViewColumn.

See also \helpref{wxDataViewRenderer}{wxdataviewrenderer}.

\membersection{wxDataViewColumn::GetSortable}\label{wxdataviewcolumngetsortable}

\func{bool}{GetSortable}{\void}

Returns true if the column is sortable.

See \helpref{SetSortable}{wxdataviewcolumnsetsortable}

\membersection{wxDataViewColumn::GetWidth}\label{wxdataviewcolumngetwidth}

\func{int}{GetWidth}{\void}

Returns the width of the column.

\membersection{wxDataViewColumn::IsSortOrderAscending}\label{wxdataviewcolumnissortorderascending}

\func{bool}{IsSortOrderAscending}{\void}

Returns true, if the sort order is ascending.

See also \helpref{SetSortOrder}{wxdataviewcolumnsetsortorder}

\membersection{wxDataViewColumn::SetAlignment}\label{wxdataviewcolumnsetalignment}

\func{void}{SetAlignment}{\param{wxAlignment }{align}}

Set the alignment of the column header.

\membersection{wxDataViewColumn::SetBitmap}\label{wxdataviewcolumnsetbitmap}

\func{void}{SetBitmap}{\param{const wxBitmap\& }{bitmap}}

Set the bitmap of the column header.

\membersection{wxDataViewColumn::SetSortOrder}\label{wxdataviewcolumnsetsortorder}

\func{void}{SetSortOrder}{\param{bool }{ascending}}

Indicate the sort order if the implementation of the
wxDataViewCtrl supports it, most commonly by showing
a little arrow. Use this in conjunction with 
\helpref{wxDataViewSortedListModel::SetAscending}{wxdataviewsortedlistmodelsetascending}
to sort the actual data.

\membersection{wxDataViewColumn::SetSortable}\label{wxdataviewcolumnsetsortable}

\func{void}{SetSortable}{\param{bool }{sortable}}

Indicate that the column is sortable. This is only to provide a
visual hint in the column (such as a sort order indicator). It
will not actually sort the data. Use a 
\helpref{wxDataViewSortedListModel}{wxdataviewsortedlistmodel}
to so the sorting.

\membersection{wxDataViewColumn::SetTitle}\label{wxdataviewcolumnsettitle}

\func{void}{SetTitle}{\param{const wxString\& }{title}}

Set the title of the column header to {\it title}.

