\section{\class{wxStdDialogButtonSizer}}\label{wxstddialogbuttonsizer}

This class creates button layouts which conform to the standard button spacing and ordering defined by the platform
or toolkit's user interface guidelines (if such things exist). By using this class, you can ensure that all your
standard dialogs look correct on all major platforms. Currently it conforms to the Windows, GTK+ and Mac OS X
human interface guidelines.

When there aren't interface guidelines defined for a particular platform or toolkit, wxStdDialogButtonSizer reverts
to the Windows implementation. 

To use this class, first add buttons to the sizer by calling AddButton (or SetAffirmativeButton, SetNegativeButton,
or SetCancelButton) and then call Realize in order to create the actual button layout used. Other than these special
operations, this sizer works like any other sizer. 

If you add a button with wxID\_SAVE, on Mac OS X the button will be renamed to "Save" and
the wxID\_NO button will be renamed to "Don't Save" in accordance with the Mac OS X Human Interface Guidelines.

\wxheading{Derived from}

\helpref{wxBoxSizer}{wxboxsizer}\\
\helpref{wxSizer}{wxsizer}\\
\helpref{wxObject}{wxobject}

\wxheading{Include files}

<wx/sizer.h>

\wxheading{See also}

\helpref{wxSizer}{wxsizer}, \helpref{Sizer overview}{sizeroverview}, \helpref{wxDialog::CreateButtonSizer}{wxdialogcreatebuttonsizer}

\membersection{wxStdDialogButtonSizer::wxStdDialogButtonSizer}\label{wxstddialogbuttonsizerctor}

\func{}{wxStdDialogButtonSizer}{\void}

Constructor for a wxStdDialogButtonSizer.

\membersection{wxStdDialogButtonSizer::AddButton}\label{wxstddialogbuttonsizeraddbutton}

\func{void}{AddButton}{\param{wxButton* }{button}}

Adds a button to the wxStdDialogButtonSizer. The button must have one of the following identifiers:

\begin{itemize}\itemsep=0pt
\item wxID\_OK
\item wxID\_YES
\item wxID\_SAVE
\item wxID\_APPLY
\item wxID\_NO
\item wxID\_CANCEL
\item wxID\_HELP
\item wxID\_CONTEXT\_HELP
\end{itemize}

\membersection{wxStdDialogButtonSizer::Realize}\label{wxstddialogbuttonsizerrealize}

\func{void}{Realize}{\void}

Rearranges the buttons and applies proper spacing between buttons to make them match the platform or toolkit's interface guidelines.

\membersection{wxStdDialogButtonSizer::SetAffirmativeButton}\label{wxstddialogbuttonsizersetaffirmativebutton}

\func{void}{SetAffirmativeButton}{\param{wxButton* }{button}}

Sets the affirmative button for the sizer. This allows you to use identifiers other than the standard identifiers outlined above.

\membersection{wxStdDialogButtonSizer::SetCancelButton}\label{wxstddialogbuttonsizersetcancelbutton}

\func{void}{SetCancelButton}{\param{wxButton* }{button}}

Sets the cancel button for the sizer. This allows you to use identifiers other than the standard identifiers outlined above.

\membersection{wxStdDialogButtonSizer::SetNegativeButton}\label{wxstddialogbuttonsizersetnegativebutton}

\func{void}{SetNegativeButton}{\param{wxButton* }{button}}

Sets the negative button for the sizer. This allows you to use identifiers other than the standard identifiers outlined above.

