\chapter{Classes by category}\label{classesbycat}
\setheader{{\it CHAPTER \thechapter}}{}{}{}{}{{\it CHAPTER \thechapter}}%
\setfooter{\thepage}{}{}{}{}{\thepage}%

A classification of FL classes by category.

{\large {\bf Plugin classes}}

Plugins can be added to frame layouts to extend behaviour.

\twocolwidtha{6cm}
\begin{twocollist}\itemsep=0pt
\twocolitem{\helpref{cbAntiflickerPlugin}{cbantiflickerplugin}}{Double-buffering class}
\twocolitem{\helpref{cbBarDragPlugin}{cbbardragplugin}}{Implements drag behaviour.}
\twocolitem{\helpref{cbBarHintsPlugin}{cbbarhintsplugin}}{Implements bar decoration and sizing behaviour.}
\twocolitem{\helpref{cbHintAnimationPlugin}{cbhintanimationplugin}}{Draws animated hints when the user drags a pane.}
\twocolitem{\helpref{cbPaneDrawPlugin}{cbpanedrawplugin}}{Implements most of MFC-style control bar implementation.}
\twocolitem{\helpref{cbPluginBase}{cbpluginbase}}{Abstract base class for all control-bar related plugins.}
\twocolitem{\helpref{cbRowDragPlugin}{cbrowdragplugin}}{Implements row-dragging functionality.}
\twocolitem{\helpref{cbRowLayoutPlugin}{cbrowlayoutplugin}}{Implements row layout functionality.}
\twocolitem{\helpref{cbSimpleCustomizationPlugin}{cbsimplecustomizationplugin}}{Enables customization of a bar.}
\twocolitem{\helpref{cbBarSpy}{cbbarspy}}{Helper class used for spying for unhandled mouse events on control bars and forwarding them to the frame layout.}
\end{twocollist}

{\large {\bf Window classes}}

Windows classes (note that the mini-button implementations are not true windows
in that they do not derive from wxWindow).

\twocolwidtha{6cm}
\begin{twocollist}\itemsep=0pt
\twocolitem{\helpref{wxToolWindow}{wxtoolwindow}}{A small frame that paints its own titlebar.}
\twocolitem{\helpref{cbFloatedBarWindow}{cbfloatedbarwindow}}{A kind of wxToolWindow implementing floating windows.}
\twocolitem{\helpref{cbMiniButton}{cbminibutton}}{Base class for wxToolWindow titlebar buttons.}
\twocolitem{\helpref{cbCloseBox}{cbclosebox}}{Close button for wxToolWindow titlebar.}
\twocolitem{\helpref{cbCollapseBox}{cbcollapsebox}}{Collapse button for wxToolWindow titlebar.}
\twocolitem{\helpref{cbDockBox}{cbdockbox}}{Dock button for wxToolWindow titlebar.}
\twocolitem{\helpref{cbCloseBox}{cbclosebox}}{Close button for wxToolWindow titlebar.}
\twocolitem{\helpref{wxNewBitmapButton}{wxnewbitmapbutton}}{Alternative bitmap button class.}
\end{twocollist}

{\large {\bf Layout management classes}}

These classes relate to the layout management framework.

\twocolwidtha{6cm}
\begin{twocollist}\itemsep=0pt
\twocolitem{\helpref{cbDockPane}{cbdockpane}}{Manages containment and control of bars in a prent frame.}
\twocolitem{\helpref{BagLayout}{baglayout}}{BagLayout lays out items in left-to-right order from top to bottom.}
\twocolitem{\helpref{cbUpdatesManagerBase}{cbupdatesmanagerbase}}{An abstract interface for display update optimization logic.}
\twocolitem{\helpref{cbSimpleUpdatesMgr}{cbsimpleupdatesmgr}}{Implements optimized logic for refreshing areas of frame layout that need to be updated.}
\twocolitem{\helpref{cbGCUpdatesMgr}{cbgcupdatesmgr}}{Implements optimized logic for refresh, based on a garbage collection algorithm.}
\twocolitem{\helpref{GarbageCollector}{garbagecollector}}{A garbage collection algorithm for use in display refresh optimization.}
\twocolitem{\helpref{wxFrameLayout}{wxframelayout}}{Manages containment and docking of control bars, which can be docked along the top, bottom, right, or left side of the parent frame.}
\end{twocollist}

{\large {\bf Event classes}}

Events are used to decouple parts of the layout framework. For event macros and identifiers,
please see the topic \helpref{Event macros and identifiers}{events}.

\twocolwidtha{6cm}
\begin{twocollist}\itemsep=0pt
\twocolitem{\helpref{cbCustomizeBarEvent}{cbcustomizebarevent}}{Class for bar customization events.}
\twocolitem{\helpref{cbCustomizeLayoutEvent}{cbcustomizelayoutevent}}{Class for layout customization events.}
\twocolitem{\helpref{cbDrawBarDecorEvent}{cbdrawbardecorevent}}{Class for bar decoration drawing events.}
\twocolitem{\helpref{cbDrawBarHandlesEvent}{cbdrawbarhandlesevent}}{Class for bar handles drawing events.}
\twocolitem{\helpref{cbDrawHintRectEvent}{cbdrawhintrectevent}}{Class for hint-rectangle drawing events.}
\twocolitem{\helpref{cbDrawPaneBkGroundEvent}{cbdrawpanebkgroundevent}}{Class for pane background drawing events.}
\twocolitem{\helpref{cbDrawPaneDecorEvent}{cbdrawpanedecorevent}}{Class for pane decoration drawing events.}
\twocolitem{\helpref{cbDrawRowBkGroundEvent}{cbdrawrowbkgroundevent}}{Class for row background drawing events.}
\twocolitem{\helpref{cbDrawRowDecorEvent}{cbdrawrowdecorevent}}{Class for row decoration drawing events.}
\twocolitem{\helpref{cbDrawRowHandlesEvent}{cbdrawrowhandlesevent}}{Class for row handles drawing events.}
\twocolitem{\helpref{cbFinishDrawInAreaEvent}{cbfinishdrawinareaevent}}{Class for finish drawing in area events.}
\twocolitem{\helpref{cbInsertBarEvent}{cbinsertbarevent}}{Class for bar insertion events.}
\twocolitem{\helpref{cbLayoutRowEvent}{cblayoutrowevent}}{Class for single row layout events.}
\twocolitem{\helpref{cbLayoutRowsEvent}{cblayoutrowsevent}}{Class for multiple rows layout events.}
\twocolitem{\helpref{cbLeftDClickEvent}{cbleftdclickevent}}{Class for mouse left double click events.}
\twocolitem{\helpref{cbLeftDownEvent}{cbleftdownevent}}{Class for mouse left down events.}
\twocolitem{\helpref{cbLeftUpEvent}{cbleftupevent}}{Class for mouse left up events.}
\twocolitem{\helpref{cbMotionEvent}{cbmotionevent}}{Class for mouse motion events.}
\twocolitem{\helpref{cbPluginEvent}{cbpluginevent}}{Base class for all control-bar plugin events.}
\twocolitem{\helpref{cbRemoveBarEvent}{cbremovebarevent}}{Class for bar removal events.}
\twocolitem{\helpref{cbResizeBarEvent}{cbresizebarevent}}{Class for bar resize events.}
\twocolitem{\helpref{cbResizeRowEvent}{cbresizerowevent}}{Class for row resize events.}
\twocolitem{\helpref{cbRightDownEvent}{cbrightdownevent}}{Class for mouse right down events.}
\twocolitem{\helpref{cbRightUpEvent}{cbrightupevent}}{Class for mouse right up events.}
\twocolitem{\helpref{cbSizeBarWndEvent}{cbsizebarwndevent}}{Class for bar window resize events.}
\twocolitem{\helpref{cbStartBarDraggingEvent}{cbstartbardraggingevent}}{Class for start-bar-dragging events.}
\twocolitem{\helpref{cbStartDrawInAreaEvent}{cbstartdrawinareaevent}}{Class for start drawing in area events.}
\end{twocollist}

